---
title: "Escapement Goals Evaluation"
author: "Kelsey Griffin"
date: "October 17, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(dplyr)
```

#Prepare Daily Escapement Data

Daily data sourced from [Alaska Department of Fish and Game. 2017. Daily salmon escapement counts from the OceanAK database, Alaska, 1921-2017. Knowledge Network for Biocomplexity. doi:10.5063/F1TX3CKH](http://doi:10.5063/F1TX3CKH)

+ filter for Bristol Bay Sockeye
+ summarize by year, calculating total count


```{r}
daily_escape<- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af119a05b-bbe7-4aea-93c6-85434dcb1c5e", method = "libcurl"),
                    stringsAsFactors = FALSE)
head(daily_escape)

```
```{r}
bbcounts <- daily_escape %>%
  filter(SASAP.Region == "Bristol Bay", Species == "Sockeye") %>% 
  separate(sampleDate, into = c("year", "month", "day")) %>% 
  group_by(year, Location) %>% 
  summarise(total_escape = sum(DailyCount))
head(bbcounts)
```

#Prepare Escapement Goals Data

Source data from [Andrew Munro and Eric Volk. 2017. Summary of Pacific Salmon Escapement Goals in Alaska with a Review of Escapements from 2007 to 2015. Knowledge Network for Biocomplexity. doi:10.5063/F1TQ5ZRG](http://doi:10.5063/F1TQ5ZRG)

+ filter for Bristol Bay Sockeye

```{r}
escape_goals<- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/knb.92014.1", method = "libcurl"),
                    stringsAsFactors = FALSE)
head(escape_goals)
```

```{r}
bb_goals <- escape_goals %>% 
  filter(Region == "Bristol Bay", Species == "Sockeye") %>% 
  select(Region, System, Lower, Upper) %>% 
  mutate(Lower = ifelse(Lower == "eliminated", NA, Lower))
head(bb_goals)


```

```{r}
test <-as.numeric(bb_goals$Lower)
  i <- which(is.na(test) == T)
print(i)
```
#Evaluate Escapement Goals

+ left join escapement data and escapement goals
+ mutate for escapement goal met

```{r}
bb_joined <- left_join(bbcounts, bb_goals, by = c("Location" = "System"))

head(bb_joined)

```

```{r}
bb_eval <- bb_joined %>% 
  mutate(goal_met = ifelse(total_escape >= Lower & total_escape <= Upper, TRUE, FALSE)) 
head(bb_eval)
  
```